Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-13 sports_analytics.Rmd
forgot to push these

Another framework for estimating expected points in basketball was proposed by @Sicilia2019DeepHoops. 
The authors first consider a classification model which returns the probabilities for whether a player would commit a foul (shooting and non-shooting), turnover, or attempt a shot. 
The values associated with each of those "terminal actions" are then utilized to compute the expected points within a basketball play.

>>>>

Another framework for estimating expected points in basketball was proposed by @Sicilia2019DeepHoops. 
The authors offer a different point of view on expected points, where they first consider a classification model which returns the probabilities for whether a player would commit a foul (shooting and non-shooting), turnover, or attempt a shot. 
The values associated with each of those "terminal actions" are then utilized to compute the expected points within a basketball play.
